---
title: "Report - Pharma"
author: "Author"
date: "23/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Report : Data Analysis of the NanoString assay.

## The Goal

Please insert here an appropriate purpose for your analysis of the Raw data.

## Quality control

the Heat Map showing positive and negative control genes in columns and samples in rows.

```{r echo = FALSE, message = FALSE, include=FALSE}

library(nanostringr)
library(gplots)
library(RColorBrewer)

reacc <- read_rcc("csdata")
reacc

b = as.data.frame(reacc$exp)

a <- reacc$raw
a <- as.data.frame(a)
dt = a[a$Code.Class == "Negative" | a$Code.Class == "Positive",]

# Rename rows by Name
rownames(dt) <- dt$Name

# Subset the dataset
dt <- subset(dt,select=-c(Name,Accession, Code.Class))

# Create the matrix input
input = as.matrix(dt)

# Colors
condition_colors <- rainbow(ncol(input), start = 0, end = .3)
```

```{r echo = FALSE, message = FALSE}

# The heatmap
heatmap(input, col=bluered(20), cexRow=1, cexCol=1, margins = c(20,13), ColSideColors=condition_colors, scale="row")
```

## Data Analysis

Boxplots of summary statistics for the two genes of interest : MCL1 and CXCL1

```{r pressure, echo=FALSE}
# Prepare data before data analysis
baseline = c("GSM2055824_02_4355_PD_mRNA", "GSM2055826_04_4078_PD_mRNA", "GSM2055828_06_3746_PD_mRNA", "GSM2055830_08_3790_PD_mRNA", "GSM2055832_10_4050_PD_mRNA")
posttraitement = c("GSM2055823_01_4353_PD_mRNA", "GSM2055825_03_3366_PD_mRNA", "GSM2055827_05_4846_PD_mRNA", "GSM2055829_07_3760_PD_mRNA", "GSM2055831_09_4436_PD_mRNA")

# data manipulation: transform columns indicating file's names to row values.
library(reshape2)
data = a[a$Name == "MCL1" | a$Name == "CXCL1",]
data = melt(data = data, id=c("Code.Class","Name", "Accession"))
# Add column : Timepoint
data = transform(data, Timepoint = ifelse(is.element(variable,baseline) == 1, "Baseline", "Post traitement"))

# BOXPLOT
boxplot(value~Timepoint*Name,data=data, main="Boxplots", xlab="TimePoint", ylab="Value")
```

The summary statistics show in the boxplots

```{r echo=FALSE}
# SUMMARY
tapply(data$value, data$Name, summary)
```
